% Metódy inžinierskej práce

\documentclass[10pt,twoside,slovak,a4paper]{article}

\usepackage[slovak]{babel}
%\usepackage[T1]{fontenc}
\usepackage[IL2]{fontenc} % lepšia sadzba písmena Ľ než v T1
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{url} % príkaz \url na formátovanie URL
\usepackage{hyperref} % odkazy v texte budú aktívne (pri niektorých triedach dokumentov spôsobuje posun textu)

\usepackage{cite}
%\usepackage{times}

\pagestyle{headings}

\title{Algorithms for advertising products, goods and services on social networks\thanks{Semestrálny projekt v predmete Metódy inžinierskej práce, ak. rok 2024/25, vedenie: Meno Priezvisko}} % meno a priezvisko vyučujúceho na cvičeniach

\author{Mykola Verkhivskyi\\[2pt]
	{\small Slovenská technická univerzita v Bratislave}\\
	{\small Fakulta informatiky a informačných technológií}\\
	{\small \texttt{xverkhivskyi@stuba.sk}}
	}

\date{\small 01. october 2024} % upravte



\begin{document}

\maketitle

\begin{abstract}
Now a lots of people want to make money and a good way would be to sell their goods and products, as well as provide services. But to achieve success you need good advertising and knowledge of the principles of its work. In this article I will describe the structure of the work of algorithms of advertising products, goods and services. You will read about a lot of interesting things such as: the principles of operation of advertising algorithms in TikTok, Instagram, Facebook, YouTube; types of advertising offers on social networks; algorithm for selecting advertising based on your interests; how to set up advertising on social networks and about situations when these algorithms will help you. This article will tell you about all the details and immerse you in the intricacies of how algorithms work, so that you can use this knowledge for your needs. After reading this article, you will have information about advertising algorithms on social networks and will know how to work with them. Reading this article is suitable for those who want to know more about advertising algorithms and then use them.
\end{abstract}



\section{Introduction}
\section{Types of advertising} \label{ešte}
\section{Operating principles} \label{nejaka}
\section{Advertising based on interests} \label{ešte}
\section{Advertising setup} \label{ešte}
\section{Conclusion} \label{dolezitejsia}
\section{References} \label{zaver} % prípadne iný variant názvu
\end{document}
